Selective electroporation of the viral envelope

### 2021-04-21 documents/pure_electroporation.tex
Big attempt
Very large problem size

The idea of inactivating viruses via electric fields is not new. Very recently, Osorio \cite{Receptor2021} have reported on a susceptibility of SARS-CoV-2's spike proteins to intense electric fields; however, in general, techniques targeting proteins appear to require truly extreme; in their study, fields of up to 2.9 GV/m were required. Dissocation of capsid proteins has been predicted by Man \cite{Picosecond2016b} at 2 GV/m. Similar techniques Tsen \cite{Studies2014}, but these have not been replicated \cite{No2011}. These regimes of intensity may possibly be accessible via ultrashort optical techniques.

@@

Of course, unlike localized tumors, viral infections are systemic, affecting many of the most favoured organs. However, either blood

Note that, despite clear evidence in nanosecond review, microsecond in vivo and clinical treatment, nanosecond in vivo conduction, and, The NATO review of vivo data regarding non-contact, "electrodeless", even above the thresholds that might otherwise be expected to cause electroporation. has not yet found any evidence demonstrating electroporation via pulsed RF. de Seze,

@@

This bears considerable similarity to e.g. radar waveform design and compressed sensing, and also problems of optimal control. In many cases, the optimal control is equal to the transfer function

@@

@@

For PSOPT, a further modification was needed, as the library does not support the derivative of the control.

Initial guess of 0 produces a trap.

because the problem depends on the second derivative of sub-nanosecond curves, the scaling varies by about 30 orders of magnitude.
PSOPT [] with IPOPT\cite{implementation2006} solver. PSOPT has the advantage of semi-automatic scaling based on bounds.

@@

It was found very useful to test the

@@

>>>>

The idea of inactivating viruses via electric fields is not new. Very recently, Osorio \cite{Receptor2021} have reported on a susceptibility of SARS-CoV-2's spike protein to intense electric fields; however, in general, techniques targeting proteins appear to require truly extreme; in their study, fields of up to 2.9 GV/m were required. Dissocation of capsid proteins has been predicted by Man \cite{Picosecond2016b} at 2 GV/m.

These regimes of intensity may possibly be accessible via ultrashort optical techniques. Similarly, Tsen \cite{Studies2014} report a non-electroporative mechanism, but these results have not been replicated at that intensity\cite{No2011}.

@@

Of course, unlike localized tumors, viral infections are systemic, affecting many of the most favoured organs.

Note that, despite clear evidence in [nanosecond review], microsecond in vivo and clinical treatment, nanosecond in vivo conduction, and, The NATO review of vivo data regarding non-contact, "electrodeless", even above the thresholds that might otherwise be expected to cause electroporation. has not yet found any evidence demonstrating electroporation via pulsed RF. de Seze,

@@

This bears considerable similarity to e.g. radar waveform design and compressed sensing, and also problems of coherent control in quantum systems. In many cases, the optimal control is equal to the transfer function

single input, multiple output

"Underactuated";

@@

\subsection{direct method Pseudospectral solvers}

@@

For PSOPT, a further modification was needed, as the library does not support the derivative of the control; the second derivative was used as the control.

because the problem depends on the second derivative of sub-nanosecond curves, the scaling varies by about 20 orders of magnitude.
PSOPT [] with IPOPT\cite{implementation2006} solver. PSOPT has the advantage of semi-automatic scaling based on supplied bounds.

@@

It was found very useful to test the equation setup by first propagating a test using a standard integrator (PSOPT's rk4 or mode 4).

@@

First the objective function with an integral power constraint was used, but this did not yield
